---
title: R in 3 Months Week 7 (Tidy Data)
format:
  rfortherestofus-slides-revealjs:
    menu: false
    progress: true
    slide-number: true
    show-slide-number: print
    center: true
    incremental: true
    auto-animate: true
execute: 
  message: false
  warning: false
  cache: false
  # eval: false
  echo: true
title-slide-attributes:
  data-background-image: assets/rru-hex-bg-gradient-dark.svg
  data-background-size: cover
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: false
library(tidyverse)
library(palmerpenguins)
library(googlesheets4)
library(janitor)
library(scales)
```

# Agenda

1. Housekeeping

1. Git + GitHub Tips

1. Tidy Data

1. Next week

::: {.notes}
https://rin3fall2023.rfortherestofus.com/slides-week-07.html
:::

# Housekeeping

- There are some more advanced exercises in the #challenges-exercises channel in Discord

- We will also be adding some more advanced exercises to lessons in the R in 3 Months Fall 2023 course

- If you're looking for more exercises, check out [R for Data Science](https://r4ds.hadley.nz/)

- Co-working sessions will no longer happen - unless you ask for it! 

# Git + GitHub Tips {.inverse}

## GitHub Desktop Wording is Confusing

## Don't Combine Git and Dropbox/OneDrive/Google Drive

::: {.fragment}
Dropbox and friends make many copies of files, which will confuse Git
:::

## How to Set up Git and GitHub in RStudio

1. Install Git (GitHub Desktop does this for you)

2. Configure Git

::: {.fragment}
```{r}
usethis::use_git_config(user.name = "David Keyes", 
                        user.email = "david@rfortherestofus.com")
```
:::

3. Create a personal access token (PAT)

::: {.fragment}
```{r}
usethis::create_github_token()
```
:::

4. Register your PAT!

::: {.fragment}
```{r}
#| eval: false
gitcreds::gitcreds_set()
```
:::

## Collaborating with GitHub

- How to get others' code

- Save, commit, pull, push

- Merge conflicts

# Tidy Data {.inverse}

# What Questions Do You Have About Tidy Data? {.inverse}

::: {.notes}
https://rfortherestofus.com/2022/01/tidy-data-chat
:::

## Gracielle's Tidy Data Example

## Libby's Tidy Data Example

## David's Top Tidy Data Tips

1. Think about your unit of analysis (e.g. individuals, responses to a question, etc) and tidy your data based on this

1. Breaking your data into multiple data frames is often an important first step

## Next Week

1. Lessons on data merging and functions

1. Project assignment: tidy your data

1. Time change in some places next week!





