---
title: R in 3 Months Week 4 (Quarto)
format:
  rfortherestofus-slides-revealjs:
    menu: false
    progress: true
    slide-number: true
    show-slide-number: print
    center: true
    incremental: true
    auto-animate: true
execute: 
  message: false
  warning: false
  cache: false
  # eval: false
  echo: true
title-slide-attributes:
  data-background-image: assets/rru-hex-bg-gradient-dark.svg
  data-background-size: cover
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: false
library(tidyverse)
library(palmerpenguins)
```

# Agenda

1. Housekeeping

1. Quarto Exercise

1. Quarto Tips

1. General Tip

1. Next week

::: {.notes}
https://rin3fall2023.rfortherestofus.com/slides-week-04.html
:::



# Housekeeping

1. When you submit project assignments, in order to keep the workload manageable for Libby and Gracielle, please limit yourself to 1 or 2 questions

1. If you have additional or more advanced questions you want help with, please post in Discord!

# Quarto {.inverse}

# Quarto Exercise {.inverse}

## Quarto Exercise

1. Copy the code from [this Quarto document](https://raw.githubusercontent.com/rfortherestofus/rin3-fall-2023/main/misc/no-render.qmd). Figure out why it won't render and change it so that it will!

1. Copy the code from [this second Quarto document](https://raw.githubusercontent.com/rfortherestofus/rin3-fall-2023/main/misc/guess-what.qmd). There are a series of questions in it. Tackle them one by one, making changes to the document as you do so.



# Quarto Tips {.inverse}

::: {.notes}
Talk about parameterized reporting making it worth it
:::

## Markdown Text Shows Up in Many Places!

1. Discord

1. Lesson comments

## Quarto Tips

## How to structure your Quarto documents

1. Load packages at top

1. Import data at top

1. Code chunks used to make outputs (graphs, tables, maps, etc)

1. I also do data cleaning/tidying in a separate R script file (you'll learn about this soon)

## How to load code in R script files

## How to change the size of plots in Quarto documents

::: {.notes}
```{r}
penguins |> 
  count(island) |> 
  ggplot(aes(x = island, 
             y = n)) +
  geom_col()
```
:::

## How to make multi-column layouts in Quarto documents

## How to change the look and feel of Quarto documents

::: {.notes}
Custom CSS: https://quarto.org/docs/output-formats/html-basics.html#css-styles

HTML Themes: https://quarto.org/docs/output-formats/html-themes.html
:::



# General Tip {.inverse}

## How to Make Sense of R Help Docs

> I looked into the geomtextpath package and even found a fairly helpful guide (https://cran.r-project.org/web/packages/geomtextpath/vignettes/geomtextpath.html) but I'm still at a loss on how to incorporate the names into the lines themselves. I wish I were better at understanding the Help guides. 

# Next Week

- Catch-up week! No live session but co-working sessions are happening.

- For following week, you will be learning to use Git and GitHub. Lessons are up now so you can start whenever you would like to!
