---
title: "R in 3 Months: Week 13 (Wrap-up)"
output:
  xaringan::moon_reader:
    css: ["style.css", "default"]
    lib_dir: libs
    df_print: paged
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE, eval = TRUE}
options(htmltools.preserve.raw = FALSE)
library(tidyverse)
library(fivethirtyeight)
library(readxl)
library(janitor)
library(patchwork)
library(here)
library(gapminder)
library(gt)
library(ggtext)
library(wakefield)
```

# Agenda

--

1. How to structure an entire project

--

1. How far you've come

--

1. Where to ask questions

--

1. How to ask good questions

--

1. Next steps


---

class: inverse, center, middle

# How to structure an entire project

???

Follow the code [here](https://github.com/rfortherestofus/rin3-spring-2023-sample-project)

---

class: inverse, center, middle

# How far you've come

---



```{r echo = FALSE, warning=FALSE, message=FALSE}
library(googlesheets4)
library(tidyverse)
library(janitor)
library(scales)

pre_survey <- read_sheet("https://docs.google.com/spreadsheets/d/19Ny92IGg0ZzIqiLs7QywaGF-Y85HQZn1iIIXN4I_tpg/edit?resourcekey#gid=1201619159") %>% 
  clean_names() %>% 
  filter(timestamp > as.Date("2023-01-01")) %>% 
  select(-what_is_your_name)

pre_survey_tidy <- pre_survey %>% 
  select(contains("rate"), contains("terrified")) %>% 
  set_names(c("data_analysis", "visualization", "scared")) %>% 
  pivot_longer(cols = everything()) %>% 
  mutate(timing = "Pre")

post_survey <- read_sheet("https://docs.google.com/spreadsheets/d/1D9UrJBp_He3Cl3rGc6-JeuwRjLQ0p6uUmM4NS__RT-8/edit?resourcekey#gid=638091153") %>% 
  clean_names() %>% 
  filter(timestamp > as.Date("2023-01-01"))

post_survey_tidy <- post_survey %>% 
  select(contains("rate"), contains("terrified")) %>% 
  set_names(c("data_analysis", "visualization", "scared")) %>% 
  pivot_longer(cols = everything()) %>% 
  mutate(timing = "Post")

pre_post_data <- bind_rows(pre_survey_tidy, post_survey_tidy) %>% 
    group_by(timing, name) %>% 
    summarize(avg_response = mean(value, na.rm = TRUE)) %>% 
    ungroup() %>% 
    mutate(timing = fct_rev(timing)) %>% 
    mutate(avg_response_formatted = number(avg_response, 0.1))

pre_post_plot <- function(area) {
   pre_post_data %>% 
    filter(name == area) %>% 
    ggplot(aes(timing, avg_response,
               color = timing,
               group = 1,
               label = avg_response_formatted)) +
    geom_line(color = "grey") +
    geom_point(size = 10) +
    geom_text(color = "white") +
    theme_minimal(base_family = "Inter") +
    theme(panel.grid.minor = element_blank(),
          axis.title = element_blank(),
          legend.position = "none") +
    scale_y_continuous(limits = c(1, 10),
                       breaks = seq(1, 10, 1)) +
    scale_color_manual(values = rev(c("#6cabdd", "#ff7400")))
}
```


## Data Analysis


```{r echo = FALSE, warning=FALSE, message=FALSE, dpi = 300, fig.height=3}
pre_post_plot("data_analysis")
```

---

## Data Visualization

```{r echo = FALSE, warning=FALSE, message=FALSE, dpi = 300, fig.height=3}
pre_post_plot("visualization")
```

---

## How Scared/Excited You Are to Learn R


```{r echo = FALSE, warning=FALSE, message=FALSE, dpi = 300, fig.height=3}
pre_post_plot("scared")
```



---

class: inverse, center, middle

# Where to ask questions

---

## Where to ask questions

There are three popular question and answer communities for (R) code questions:

---

## [stackoverflow.com](https://stackoverflow.com)

- This is a general purpose code Q&A website.

- Unfortunately, it has a well-earned reputation for not being welcoming to new users.

---

## [Posit Community](https://community.rstudio.com/)

- This community is run by RStudio and is specifically for R users.

- The admins do work to make the site a welcoming place for all users.

---

## [R for Data Science Learning Community](https://www.rfordatasci.com/)

- Slack community that is very welcoming to newbies

- Has regular office hours where you can get 1-on-1 help

---

## Bonus: [R-Ladies](https://rladies.org/)

- "A worldwide organization whose mission is to promote gender diversity in the R community"

- Extremely welcoming

- Have local chapters that often host events

---

class: inverse, center, middle

# How to ask good (code) questions

---

## How to ask good (code) questions

The most important part of asking good questions about code is to provide **reproducible examples**.

> A **reproducible example** contains all necessary code to reproduce your error or to customise your chart.

The `reprex` package is designed to help guarantee your examples are reproducible.

---

## Good code examples are *minimal*

In addition to making your code reproducible you should try to make it *minimal*.

--

> Use the smallest, simplest, most built-in data possible.
> 
> Think: iris or mtcars. Bore me.

--

Make your question as focused as possible

---

## Example of good repex

How can I make my x axis text better?

```{r echo = FALSE, fig.height = 3, dpi = 150}
mtcars %>% 
  group_by(cyl) %>% 
  summarize(avg_horsepower = mean(hp)) %>% 
  ggplot(aes(x = cyl,
             y = avg_horsepower)) +
  geom_col()
```

---


## Using the `reprex` package

1. Select the code that makes your reprex

1. Open the Addins menu and select "Render reprex..."

1. Choose the options for where you're asking your question

1. Copy and paste the output in the Viewer tab into your question

---

## Learn more about reprex

[Jenny Bryan video overview of reprex](https://www.youtube.com/watch?v=5gqksthQ0cM&ab_channel=PositPBC)

[StackOverflow thread on how to write a good reprex](https://stackoverflow.com/questions/5963269/how-to-make-a-great-r-reproducible-example/16532098)


---

class: inverse, center, middle

# What happens next

---

## Your feedback

[We have a very short post-course survey](https://forms.gle/mUZqN4UXnjP53nzYA)

--

We'd also like to ask you to record a ~5min video with about something you've learned thanks to R in 3 Months and submit it on the [final project submission page](https://rfortherestofus.com/courses/r-in-3-months-spring-2023/lessons/r-in-3-months-spring-2023-final-project-assignment/).


---

## Book 1:1 sessions with Charlie

[You can book a 1:1 with Charlie from January 2023](https://savvycal.com/charliejhadley-r-for-the-rest-of-us/chat).

---

## Assignment submissions

Charlie will provide feedback on all submissions made by the end of June

--

I will be on vacation from June 14-24

---

class: middle, center, inverse

# Any final questions?


---

class: middle, center

# Thank you for making this fun!








