---
title: R in 3 Months Week 4 (Quarto)
format:
  rfortherestofus-slides-revealjs:
    menu: false
    progress: true
    slide-number: true
    show-slide-number: print
    center: true
    incremental: true
    auto-animate: true
execute: 
  message: false
  warning: false
  cache: false
  # eval: false
  echo: true
title-slide-attributes:
  data-background-image: assets/rru-hex-bg-gradient-dark.svg
  data-background-size: cover
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: false
library(tidyverse)
library(palmerpenguins)
library(googlesheets4)
library(janitor)
library(scales)
```

# Agenda

1. Housekeeping

1. Data Viz Tips

1. Git + GitHub

1. Next week

::: {.notes}
https://rin3fall2023.rfortherestofus.com/slides-week-06.html
:::

# Housekeeping {.inverse}

## What Does the Rest of R in 3 Months Look Like?

- Week 7: Advanced Data Wrangling, Part 1 (Tidy Data)

- Week 8: Advanced Data Wrangling, Part 2 (Functions and Data Merging)

- Week 9: Advanced Data Viz, Part 1 (Highlighting and Decluttering)

- Week 10: Advanced Data Viz, Part 2 (Explaining and Making Your Viz Sparkle)

- Week 11: Catch-Up Week

- Week 12: Advanced Quarto

- Week 13: Wrap Up

## Final project

- Record a 5-minute video showing what you have learned how to do in R over the three months

## You have access to materials FOREVER! {.inverse}

## Survey Results {.inverse}

## Overall Progress

```{r}
#| echo: false
gs4_auth("david@rfortherestofus.com")

check_in_data <-
  read_sheet("https://docs.google.com/spreadsheets/d/1CQp1HiDltZ9rU6AoHDUhxMWX6hD_H2Yh5XCFvkBu8-U/edit?usp=sharing") |> 
  clean_names() |> 
  filter(timestamp >= as.Date("2023-10-01"))
```

```{r}
#| echo: false
check_in_data |> 
  select(2) |> 
  set_names("progress") |> 
  count(progress) |> 
  ggplot(aes(x = progress,
             y = n,
             label = n)) +
  geom_col(fill = "#6cabdd") +
  geom_text(vjust = 1.5,
            family = "Inter Tight",
            color = "white",
            size = 16 / .pt) +
  theme_void(base_size = 16,
             base_family = "Inter Tight") +
  theme(axis.text.x = element_text()) +
  scale_y_continuous(expand = expansion(0, 0.1))
```


## Overall Workload

```{r}
#| echo: false
check_in_data |> 
  select(3) |> 
  set_names("workload") |> 
  count(workload) |> 
  mutate(workload = factor(workload,
                           levels = c("Not enough",
                                      "Just right", 
                                      "Too much"))) |> 
  ggplot(aes(x = workload,
             y = n,
             label = n)) +
  geom_col(fill = "#6cabdd") +
  geom_text(vjust = 1.5,
            family = "Inter Tight",
            color = "white",
            size = 16 / .pt) +
  theme_void(base_size = 16,
             base_family = "Inter Tight") +
  theme(axis.text.x = element_text(),
        plot.margin = margin(10, 10, 10, 10)) +
  scale_y_continuous(expand = expansion(0, 0.1))
```


## Search All Videos

> Not sure if this is an easy thing or not.. but I've found myself wanting to go back and find something that was specifically mentioned in a particular week's lessons, but wasn't sure in which video. The easiest way I could find to do this was to do a CMD+F search on every video within the lesson until I found the one that matched the text I was looking for. It would be SO awesome if there was a global search for the lessons.

<br>

::: {.small}
[Ask and you shall receive!](https://rfortherestofus.com/courses/r-in-3-months-fall-2023/lessons/all-r-in-3-months-fall-2023-videos)
:::

::: {.notes}
https://rfortherestofus.com/courses/r-in-3-months-fall-2023/lessons/all-r-in-3-months-fall-2023-videos
:::

## Ask Questions!

- If you'd rather not ask in the chat, please message David, Libby, or Gracielle privately and we'll ask anonymously on your behalf!

## Want More Advanced Materials?

1. They're coming!

1. If you have specific topics you'd like to see us address, please ask and we'll make additional lessons!

# Data Viz Tips {.inverse}

## Sizing of Plots in Preview Isn't Accurate

# Git + GitHub {.inverse}

## Git + GitHub

- Make sure you use the R Git Ignore template

- Using Git + GitHub with RStudio

- How to Reproducibly Access Data Outside of Your RStudio Project

- Publishing with GitHub Pages/Netlify

- Using GitHub for Project Management

- GitHub Actions

::: {.notes}
- https://googledrive.tidyverse.org/
- https://foodmap.apicouncil.org/
- https://github.com/rfortherestofus/rfortherestofus.com/issues
- https://rfortherestofus.com/2023/05/github-actions
:::



# Next Week

- Advanced data wrangling and analysis

- Tidy data

- No project assignment (but start thinking about how your data is or is not tidy)
