---
title: R in 3 Months Week 13 (Wrapping Up)
format:
  rfortherestofus-slides-revealjs:
    menu: false
progress: true
slide-number: true
show-slide-number: print
center: true
incremental: true
auto-animate: true
execute: 
  message: false
  warning: false
  cache: false
  # eval: false
  echo: true
title-slide-attributes:
  data-background-image: assets/rru-hex-bg-gradient-dark.svg
data-background-size: cover
editor:
  render-on-save: true
editor_options: 
  chunk_output_type: console
---

  
```{r}
#| echo: false
library(tidyverse)
library(janitor)
```


# Agenda

1. How Far You've Come

1. Where to Go From Here

::: {.notes}
https://rin3fall2023.rfortherestofus.com/slides-week-13.html
:::
  
# How Far You've Come {.inverse}

```{r}
#| echo: false

library(googlesheets4)
library(tidyverse)
library(janitor)
library(scales)

gs4_auth("david@rfortherestofus.com")

pre_survey <- read_sheet("https://docs.google.com/spreadsheets/d/19Ny92IGg0ZzIqiLs7QywaGF-Y85HQZn1iIIXN4I_tpg/edit#gid=1201619159") |>
  clean_names() |>
  filter(timestamp > as.Date("2023-09-01")) |>
  select(-what_is_your_name)

pre_survey_tidy <- pre_survey |>
  select(contains("rate"), contains("terrified")) |>
  set_names(c("data_analysis", "visualization", "scared")) |>
  pivot_longer(cols = everything()) |>
  mutate(timing = "Pre")

post_survey <- read_sheet("https://docs.google.com/spreadsheets/d/1S5g1UYyBKiUfIU3yi9M_OZs1RvedH5xPPrMhs8Sw53o/edit#gid=1400508795") |>
  clean_names() |>
  filter(timestamp > as.Date("2023-09-01"))

post_survey_tidy <- post_survey |>
  select(contains("rate"), contains("terrified")) |>
  set_names(c("data_analysis", "visualization", "scared")) |>
  pivot_longer(cols = everything()) |>
  mutate(timing = "Post")

pre_post_data <- bind_rows(pre_survey_tidy, post_survey_tidy) |>
    group_by(timing, name) |>
    summarize(avg_response = mean(value, na.rm = TRUE)) |>
    ungroup() |>
    mutate(timing = fct_rev(timing)) |>
    mutate(avg_response_formatted = number(avg_response, 0.1))

pre_post_plot <- function(area) {
   pre_post_data |>
    filter(name == area) |>
    ggplot(aes(timing, avg_response,
               color = timing,
               group = 1,
               label = avg_response_formatted)) +
    geom_line(color = "grey") +
    geom_point(size = 10) +
    geom_text(color = "white") +
    theme_minimal(base_family = "Inter") +
    theme(panel.grid.minor = element_blank(),
          axis.title = element_blank(),
          legend.position = "none") +
    scale_y_continuous(limits = c(1, 10),
                       breaks = seq(1, 10, 1)) +
    scale_color_manual(values = rev(c("#6cabdd", "#ff7400")))
}
```

::: {.notes}
https://rfortherestofus.com/courses/r-in-3-months-fall-2023/lessons/r-in-3-months-progress-survey
:::

## Data Analysis

```{r}
#| echo: false
pre_post_plot(area = "data_analysis")
```

## Data Visualization

```{r}
#| echo: false
pre_post_plot("visualization")
```



## How Scared/Excited You Are About R

```{r}
#| echo: false
pre_post_plot("scared")
```

## What You've Done in the Last Three Months {.inverse}

# Where to Go From Here {.inverse}

## Where to Ask Questions

There are three popular question and answer communities for (R) code questions:

## [stackoverflow.com](https://stackoverflow.com)

- This is a general purpose code Q&A website.

- Unfortunately, it has a well-earned reputation for not being welcoming to new users.



## [Posit Community](https://community.rstudio.com/)

- This community is run by Posit and is specifically for R users.

- The admins do work to make the site a welcoming place for all users.

## [R for Data Science Learning Community](https://www.rfordatasci.com/)

- Slack community that is very welcoming to newbies

- Has regular office hours where you can get 1-on-1 help

## Bonus: [R-Ladies](https://rladies.org/)

- "A worldwide organization whose mission is to promote gender diversity in the R community"

- Extremely welcoming

- Have local chapters that often host events

## Bonus: ChatGPT

- The more you can specify the package you want it to use, the better results you'll have

# How to Ask Good (Code) Questions {.inverse}



## How to Ask Good (Code) Questions

The most important part of asking good questions about code is to provide **reproducible examples**.

. . .

> A **reproducible example** contains all necessary code to reproduce your error or to customise your chart.

. . .

The `reprex` package is designed to help guarantee your examples are reproducible.

## Examples are *Minimal*

In addition to making your code reproducible you should try to make it *minimal*.

. . .

> Use the smallest, simplest, most built-in data possible.
> 
> Think: iris or mtcars. Bore me.

. . .

Make your question as focused as possible



## Example of a Good Reprex

How can I reorder bars on the y axis?

```{r}
library(tidyverse)

diamonds |>
  mutate(cut = as.character(cut)) |>
  group_by(cut) |>
  summarize(avg_price = mean(price)) |>
  ggplot(aes(
    x = avg_price,
    y = cut
  )) +
  geom_col()
```


## Using the `reprex` Package

1. Select the code that makes your reprex

1. Open the Addins menu and select "Render reprex..."

1. Choose the options for where you're asking your question

1. Copy and paste the output in the Viewer tab into your question



## Learn More About Reprex

[Jenny Bryan video overview of reprex](https://www.youtube.com/watch?v=5gqksthQ0cM&ab_channel=PositPBC)

[StackOverflow thread on how to write a good reprex](https://stackoverflow.com/questions/5963269/how-to-make-a-great-r-reproducible-example/16532098)

# Wrapping Up {.inverse}

## R in 3 Months

1. Submit any assignments for feedback any time in December

1. Any 1-on-1s with your coaches must be completed by December 22

1. Please submit final assignments whenever (we love seeing what you've done!)

1. You have access to course materials FOREVER

## Other Things

1. Topics courses (use coupon code RIN3TOPICSCOURSES to get 25% off)

1. Additional ways that R for the Rest of Us can help you and your organization

# Thank You for Being Part of R in 3 Months! {.inverse}
